
Multirotor vehicles have recently gained widespread use in various
application areas, such as transportation, surveillance, and even
entertainment. These platforms are mechanically simple and typically
lightweight, resulting in a low cost of acquisition and
maintenance. However, to the best knowledge of the authors, there is
no known application of multirotor vehicles in space
environments. Discarding the obvious impossibility of maneuvering in
the absence of air, we consider here the use of these vehicles in
human-compatible pressurised spaces under microgravity, such as inside
inhabited space stations.

The idea of aerial vehicles inside space stations is not new. The NASA
project SPHERES (Synchronized Position Hold Engage Reorient
Experimental Satellites) started in 2000 with the design of a small
pressurised air propulsion vehicle~\cite{miller00}. In 2006 three
SPHERES units were deployed aboard the International Space Station
(ISS)~\cite{nolet07}.  However, the use of pressurised air makes the
mechanical complexity significantly higher than a multirotor based
solution.  More recently, NASA proposed the Astrobee vehicle, with a
simpler propulsion system based on several centrifugal fans and
nozzles~\cite{bualat15}. The Astrobee also features a 2 DoF arm and
docking capability.

The most prominent feature of these spaces is the absence of gravity
exerted in bodies, that is, the gravity force canceled
by the orbital motion of the air mass (microgravity). We will exploit this feature in
the following way. Most multirotor orient their propellers
vertically along parallel axes. This maximizes thrust vertically in
order to compensate for the gravity force. However, in doing so they
need to tilt in order to move sideways. Moreover, most of the energy
is spent in compensating for gravity. In its absence, not
only there is no need to compensate for gravity, but also the
energy consumption is expected to be significantly less. We propose
to orient the propeller rotation axes non-parallel among them, in
such a way we obtain a fully actuated body. That is, to be able
to decouple translational from rotational motion. We expect to
increase maneuverability, being a particularly relevant feature inside
confined spaces such as the interior of a space station.

Fully actuated multirotor have been proposed in the past, but the
literature is scarce. In~\cite{jiang13,voyles12} a dexterous
hexarotor has been proposed, where the fully actuation feature is
used for dexterous manipulation. However, this vehicle is designed for
Earth applications, and thus a tradeoff is necessary between dexterity
and gravity compensation. Our design is also based in an hexarotor,
but since we consider microgravity, we will design the propeller
orientation in order to maximize maneuverability along all directions.

The goal of this paper is to present a design of an hexarotor for
microgravity environments. We target a multipurpose vehicle, and
provide as working examples (1)~telepresence, requiring the vehicle to
manoeuvre in such a way the screen and camera is pointer towards the
party onboard, and (2)~mobile manipulation, requiring force closure in
order to compensate the reaction force at the end effector. We also
consider operational issues such as docking into a charging station
and stacking of multiple units in order to save space.

This paper is structured as follows: the requirements and
specifications we considered, including a preliminary mechanical
design for the vehicle are explained in
Section~\ref{sec:vehicle-design}, in Section~\ref{sec:dynamical-model} we
derive a parametric dynamical model of the vehicle, which is then used
in Section~\ref{sec:design-parameters} for the optimization of the
propellers orientation. Section~\ref{sec:posit-attit-contr} proposes a
convergent controller for this fully actuated vehicle, and a
preliminary validation in a realistic simulation environment is
presented in Section~\ref{sec:prel-valid}, while
Section~\ref{sec:concl-future-work} wraps up the paper with concluding
remarks and a reference for future work.


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End: 
