\documentclass[11pt,a4paper]{article}
\pdfoutput=1

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{subfig}
\usepackage{gensymb}

% COMMENT THIS LINE FOR ARXIV SUBMISSION
\graphicspath{{figs/}}

\begin{document}

\title{Space CoBot: a collaborative aerial robot for indoor microgravity
  environments}
\author{Pedro Roque}
\author{Rodrigo Ventura}
\affil{%
  Institute for Systems and Robotics \\
  Instituto Superior Técnico, Universidade de Lisboa \\
  Av. Rovisco Pais, 1; 1049-001 Lisboa, Portugal \\
  {\small pedro.roque@tecnico.ulisboa.pt} \\
  {\small rodrigo.ventura@isr.tecnico.ulisboa.pt}}
\date{}
\maketitle

\begin{abstract}
  This paper presents a first contribution to the design of a small
  aerial robot for inhabited microgravity environments, such as
  orbiting space stations. In particular, we target a fleet of robots
  for collaborative tasks with humans, such as telepresence and
  cooperative mobile manipulation. We explore a propeller based
  propulsion system, arranged in such a way that the translational and
  the rotational components can be decoupled, resulting in an holonomic
  hexarotor. Since propellers have limited thrust, we employ an
  optimization approach to select the geometric configuration
  given a criteria of uniform maximum thrust across all directions in
  the body reference frame. We also tackle the problem of motion
  control: due to the decoupling of translational and rotational modes
  we use separate converging controllers for each one of these
  modes. In addition, we present preliminary simulation results in a
  realistic simulator, in closed loop with the proposed controller,
  thus providing a first validation of the followed methodology.
\end{abstract}

\section{Introduction}
\label{sec:introduction}
\input{intro.tex}

\section{Vehicle design}
\label{sec:vehicle-design}
%UNUSED: \input{vd.tex}

\subsection{Requirements}
\label{sec:requirements}
\input{vd_requirements.tex}

\subsection{Specification}
\label{sec:specification}
\input{vd_specification.tex}

\section{Dynamical model}
\label{sec:dynamical-model}
\input{dyn_model.tex}

\section{Optimization of the design parameters}
\label{sec:design-parameters}
\input{optimization.tex}

\section{Position and attitude control}
\label{sec:posit-attit-contr}
\input{control.tex}

\section{Preliminary validation in simulation}
\label{sec:prel-valid}
\input{simulation.tex}

\section{Conclusions and future work}
\label{sec:concl-future-work}
\input{conclusion.tex}

\section*{Acknowledgments}
\label{sec:acknowledgments}

The authors are grateful to André Santos for the CAD modeling of the
vehicle and the renderings presented in this paper. This work was
supported by the FCT project~[UID/EEA/50009/2013].

\bibliography{biblio}
\bibliographystyle{plain}



\end{document}
