%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{subfig}
\usepackage{gensymb}

\graphicspath{{figs/}}


\title{\LARGE \bf
  Space CoBot: modular design of an holonomic aerial robot for indoor microgravity environments
}

\author{Pedro Roque$^{1}$ and Rodrigo Ventura$^{1}$% <-this % stops a space
\thanks{*The authors are grateful to André Santos for the CAD modeling of the
vehicle and the renderings presented in this paper. This work was
supported by the FCT project~[UID/EEA/50009/2013].}% <-this % stops a space
\thanks{$^{1}$Pedro Roque and Rodrigo Ventura are with Institute for Systems and Robotics, Instituto Superior Técnico, Universidade de Lisboa, Av. Rovisco Pais, 1, 1049-001 Lisboa, Portugal.
        {\tt\small pedro.roque@tecnico.ulisboa.pt, rodrigo.ventura@isr.tecnico.ulisboa.pt}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

  This paper presents the design of a small aerial robot for inhabited
  microgravity environments, such as orbiting space stations (e.g.,
  ISS). In particular, we target a fleet of robots, called Space
  CoBots, for collaborative tasks with humans, such as telepresence
  and cooperative mobile manipulation. The design is modular,
  comprising an hexrotor based propulsion system, and a stack of
  modules including batteries, cameras for navigation, a screen for
  telepresence, a robotic arm, space for extension modules, and a pair
  of docking ports. These ports can be used for docking and for
  mechanically attaching two Space CoBots together. The kinematics is
  holonomic, and thus the translational and the rotational components
  can be fully decoupled. We employ a multi-criteria optimization
  approach to determine the best geometric configuration for maximum
  thrust and torque across all directions. We also tackle the problem
  of motion control: we use separate converging controllers for
  position and attitude control. Finally, we present simulation
  results using a realistic physics simulator. These experiments
  include a sensitivity evaluation to sensor noise and to unmodeled
  dynamics, namely a load transportation.

\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
\label{sec:introduction}
\input{intro.tex}

\section{VEHICLE DESIGN}
\label{sec:vehicle-design}
\input{design.tex}

\section{PROPULSION MODEL}
\label{sec:propulsion}
\input{propulsion.tex}

\section{OPTIMIZATION OF THE DESIGN PARAMETERS}
\label{sec:design-parameters}
\input{optimization.tex}

\section{POSITION AND ATTITUDE CONTROL}
\label{sec:posit-attit-contr}
\input{control.tex}

\section{SIMULATION RESULTS}
\label{sec:prel-valid}
\input{simulation.tex}

\section{CONCLUSIONS AND FUTURE WORK}
\label{sec:concl-future-work}
\input{conclusion.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{ACKNOWLEDGMENT}

% The authors are grateful to André Santos for the CAD modeling of the
% vehicle and the renderings presented in this paper. This work was
% supported by the FCT project~[UID/EEA/50009/2013].


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{biblio}
\bibliographystyle{IEEEtran}


\end{document}
